The Effect of the COVID-19 Pandemic on Influenza Vaccination Rates in the United States

### 2022-12-05 Manuscript/manuscript.tex
edited sources

\begin{document}
\maketitle
\section*{Abstract}
\label{sec:Abstract}
Past research has shown that the influenza vaccination has decreased the likelihood of hospitalization within patients
that test positive for COVID-19 \citep{conlon2021impact}. Thus, maintaning high influenza vaccination rates is essential \
to decreasing the severity of COVID-19 cases. The goal of this study is to determine how influenza vaccination rates within the
United States have changed due to the pandemic by comparing proportions of those vaccinated before the pandemic, defined as 2018-2019
to those during the pandemic, defined as 2020-2021, and comparing during the pandemic to proportions after the pandemic defined as 2021-2022. 
In order to account for possible factors that influence influenza vaccination coverage, the analysis was performed on three groups: by age,
race, and the general population. Results showed that there is statistically significant evidence in favor of a difference in proportions before,
and after the COVID-19 pandemic for the various age groups and the general population. There is no statistically significant evidence of a difference
in proporitions for the racial groups.

@@

test was conducted to compare vaccination adherence change and a multinomial logistic rgression analysis was performed to assess the relationship between influenza vaccination behaviors and charactertics such as age and gender. Results indicated

@@

between not being willing to receive the next seasons influenza vaccination and socioeconomic characteristics using multivariable logistic regression. "to verify the influence of the COVID-19 pandemic on intention to be vaccinated in the 2020/21 season, 
as compared with the previous 2019/20 vaccination, an ordinal logistic regression analysis was performed with the output expressed as the adjusted proportional odds ratio (pOR)" \citep{domnich2020attitudes}. Results showed "most (74.8\%) participants valued 

@@

odds of receiving the 2020/21 season influenza vaccination. However, the COVID-19 pandemic may have positively influenced the propensity of being vaccinated against 2020/21 seasonal influenza" \citep{domnich2020attitudes}. This study suggested that there could have 

>>>>

\begin{document}
\maketitle
\section*{Abstract}
\label{sec:Abstract}
Past research has shown that the influenza vaccination has decreased the likelihood of hospitalization within patients
that test positive for COVID-19 \citep{conlon2021impact}. Thus, maintaning high influenza vaccination rates is essential
for decreasing the severity of COVID-19 cases. The goal of this study is to determine how influenza vaccination rates within the
United States have changed due to the pandemic by comparing proportions of those vaccinated before the pandemic, defined as 2018-2019
to those during the pandemic, defined as 2020-2021, and comparing during the pandemic to proportions after the pandemic defined as 2021-2022. 
In order to account for possible factors that influence influenza vaccination coverage, the analysis was performed on three groups: age,
race, and the general population. Results showed that there is statistically significant evidence in favor of a difference in proportions before,
and after the COVID-19 pandemic for the various age groups and the general population. There is no statistically significant evidence of a difference
in proporitions for the racial groups.

@@

test was conducted to compare vaccination adherence change and a multinomial logistic rgression analysis was performed to assess the relationship between influenza vaccination behaviors and charactertics such as age and gender.Results indicated

@@

between not being willing to receive the next seasons influenza vaccination and socioeconomic characteristics using multivariable logistic regression. "To verify the influence of the COVID-19 pandemic on intention to be vaccinated in the 2020-2021 season, 
as compared with the previous 2019-2020 vaccination, an ordinal logistic regression analysis was performed with the output expressed as the adjusted proportional odds ratio" \citep{domnich2020attitudes}. Results showed "most (74.8\%) participants valued 

@@

odds of receiving the 2020-2021 season influenza vaccination. However, the COVID-19 pandemic may have positively influenced the propensity of being vaccinated against 2020-2021 seasonal influenza" \citep{domnich2020attitudes}. This study suggested that there could have 
